---
title: "text vars snippet"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r text-vars}
# text vars fn by dyurovsky
make_text_vars <- function(df, term_name, term_filter = NULL) {
  if(!is.null(term_filter)) {
    filtered_df <- df %>%
      filter(term == term_filter) 
  } else{
    filtered_df <- df
  }
    
  walk(c("estimate", "statistic", "p.value"), 
      ~assign(glue("{term_name}_{.x}"), 
              filtered_df %>% pull(!!.x), 
         envir = globalenv()))
}
```

```{r model}
example_model <- data %>%
  glmer(response ~ condition1 * condition2 + (1|subid), family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  mutate(p.value = printp(p.value))

walk2(c("c1_main_effect", "c2_main_effect", "c1_c2_interaction"), # the names of the vars
      c("condition1TRUE", "condition2TRUE", "condition1TRUE:condition2TRUE"), 
      # the names of the effects in the regression table
      ~ make_text_vars(glmer_unique, .x, .y))
```

There was a main effect of the first condition manipulation ($\beta =$ `r c1_main_effect_estimate`, $t =$ `r c1_main_effect_statistic`, $p$ `r c1_main_effect_p.value`) and the second condition manipulation ($\beta =$ `r c2_main_effect_estimate` , $t =$ `r c2_main_effect_statistic`, $p$ `r c2_main_effect_p.value`). There was also an interaction between the two ($\beta =$ `r c1_c2_interaction_estimate` , $t =$ `r c1_c2_interaction_statistic`, $p$ `r c1_c2_interaction_p.value`).
